State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-09 prism-backend/research/soa_review/soa-review.tex
Thought on lack of non-frameability in ACs.

\begin{itemize}
\item Many constructions of ACs and GSs seem to be built using the same
  approach: an issuer and a user interact so that the latter receives a signature
  from the former; then the user employs that signature to do something else (in
  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
  security models are different. Concretely, GSs have a very well established
  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
  seen cover something similar to non-frameability, nor traceability, but just
  include conventional unforgeability properties. Why is this?
\end{itemize}

>>>>

\begin{itemize}
\item Many constructions of ACs and GSs seem to be built using the same
  approach: an issuer and a user interact so that the latter receives a signature
  from the former; then the user employs that signature to do something else (in
  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
  security models are different. Concretely, GSs have a very well established
  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
  seen cover something similar to non-frameability, nor traceability, but just
  include conventional unforgeability properties. Why is this?
  \begin{itemize}
  \item Concerning non-frameability, this probably is because the de-anonymizing
    functionality that ACs include (if any) is revocation, which is essentially
    a blacklisting. On the other hand, GSs usually allow opening, which extracts
    the actual identity. Opening is ``stronger'' than blacklisting, in the sense
    that it can be used to build blacklisting, but it is also more threatening
    to privacy and may have further implications. Among these, unequivocable
    framing of users. This, in general, does not seem possible with conventional
    blacklisting (or, at least, not in an unequivocable way).
  \item Concerning traceability.
  \end{itemize}
\end{itemize}
